\documentclass[a4paper]{tufte-book} % Use the tufte-book class which in turn uses the tufte-common class

\hypersetup{colorlinks} % Comment this line if you don't wish to have colored links
\usepackage{microtype} % Improves character and word spacing
\usepackage{booktabs} % Better horizontal rules in tables

\usepackage{texnames}
\usepackage{epigraph}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{bm,bbm}
\usepackage[]{subfig}
\usepackage[binary-units]{siunitx}

\usepackage[T1]{fontenc}
\usepackage{bbding}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{exer}{Exercise}[chapter]

\usepackage{listings}
\lstset{language=R}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=5pt,frame=bottomline}

\usepackage{graphicx} % Needed to insert images into the document
\graphicspath{{./Figures/}} % Sets the default location of pictures
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio} % Improves figure scaling

\usepackage{fancyvrb} % Allows customization of verbatim environments
\fvset{fontsize=\normalsize} % The font size of all verbatim text can be changed here

\newcommand{\hangp}[1]{\makebox[0pt][r]{(}#1\makebox[0pt][l]{)}} % New command to create parentheses around text in tables which take up no horizontal space - this improves column spacing
\newcommand{\hangstar}{\makebox[0pt][l]{*}} % New command to create asterisks in tables which take up no horizontal space - this improves column spacing

\newcommand{\E}{\operatorname{E}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\CV}{\operatorname{CV}}

\usepackage{xspace} % Used for printing a trailing space better than using a tilde (~) using the \xspace command

\newcommand{\monthyear}{\ifcase\month\or January\or February\or March\or April\or May\or June\or July\or August\or September\or October\or November\or December\fi\space\number\year} % A command to print the current month and year

\newcommand{\openepigraph}[2]{ % This block sets up a command for printing an epigraph with 2 arguments - the quote and the author
\begin{fullwidth}
\sffamily\large
\begin{doublespace}
\noindent\allcaps{#1}\\ % The quote
\noindent\allcaps{#2} % The author
\end{doublespace}
\end{fullwidth}
}

\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}

\newcommand{\blankpage}{\newpage\hbox{}\thispagestyle{empty}\newpage} % Command to insert a blank page

\usepackage{makeidx} % Used to generate the index
\makeindex % Generate the index which is printed at the end of the document

%----------------------------------------------------------------------------------------
%	BOOK META-INFORMATION
%----------------------------------------------------------------------------------------

\title{Operational\\ Statistics for\\ SAR Imagery} % Title of the book

\author{Alejandro C.\ Frery,
Jie Wu} % Author

\publisher{Publisher Name} % Publisher

%----------------------------------------------------------------------------------------

\begin{document}

\frontmatter

%----------------------------------------------------------------------------------------
%	EPIGRAPH
%----------------------------------------------------------------------------------------

\thispagestyle{empty}
\openepigraph{I can resist everything except temptation.}{Oscar Wilde, {\itshape Lady Windermere's Fan (1892)}}
\vfill
%\openepigraph{Quotation 2}{Author}
%\vfill
%\openepigraph{Quotation 3}{Author}

%----------------------------------------------------------------------------------------

\maketitle % Print the title page

%----------------------------------------------------------------------------------------
%	COPYRIGHT PAGE
%----------------------------------------------------------------------------------------

\newpage
\begin{fullwidth}
~\vfill
\thispagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
Copyright \copyright\ \the\year\ \thanklessauthor

\par\smallcaps{Published by Alejandro C.\ Frery}

\par\smallcaps{\url{https://github.com/acfrery/Statistics-SAR-Intensity.git
}}

\par License information.\index{license}

\par\textit{First printing, \monthyear}
\end{fullwidth}

%----------------------------------------------------------------------------------------
x
\tableofcontents % Print the table of contents

%----------------------------------------------------------------------------------------

\listoffigures % Print a list of figures

%----------------------------------------------------------------------------------------

\listoftables % Print a list of tables

%----------------------------------------------------------------------------------------
%	DEDICATION PAGE
%----------------------------------------------------------------------------------------

\cleardoublepage
~\vfill
\begin{doublespace}
\noindent\fontsize{18}{22}\selectfont\itshape
\nohyphenation
Dedicated to my husband, my family, and my friends. They are the salt of my life.
\end{doublespace}
\vfill
\vfill


\cleardoublepage
\chapter*{Foreword} % The asterisk leaves out this chapter from the table of contents

\newthought{I have been thinking} of writing this book for a long time now.
My first experience with such a challenge dates back to the eighties, with my then (and forever) advisor Prof.\ Oscar Bustos, at IMPA (\textit{Instituto de Matem\'atica Pura e Aplicada}, at Rio de Janeiro).
I learned with him the necessary mindset for writing a long piece of scientific work, and the outcome had a warm reception\cite{BustosFrery:92:ABE}.

I jumped into my second experience, during a post-doc back at IMPA, about twenty years later.
It was a completely different challenge: producing the second, and enlarged, edition of an already successful book, also with a very nice outcome\cite{IPVG:2008}.
While working on this book I started feeling the need of some kind of control version for a collaborative work.

Writing this second book I noticed that the information about image processing with \texttt R\cite{Rmanual} was scattered in half a dozen libraries, and that the experienced gained with the book might deserve writing a book, albeit a short one.
The opportunity came with a generous offer from Springer to write our \textit{Introduction to Image Processing with \texttt R: Learning by Examples}\cite{IntroImageProcessingR}.

One year before that book I received an invitation to contribute with a chapter for the book \textit{Digital Document Analysis and Processing}\cite{DigitalDocumentAnalysisProcessing}.
This challenge brought me back to the need to collaborate in a remote fashion, but this time with a team of more than twenty authors.

So I was invited this year to give a twenty-hour course on statistical tools for Synthetic Aperture Radar -- SAR imagery analysis at CONAE -- \textit{Comisi\'on Nacional de Actividades Espaciales}, Argentina.
I wanted to make a course that would leave a positive residue:
students would have the chance to learn and practice, and in order to do that I decided to use and share all the contents in \texttt{RMarkdown}.
It was a nice experience, but I felt limitations (mostly mine) with such platform.
When I was later invited to produce material for a sixty-hour distance education course, my first challenge was deciding the format.
After pondering a couple of possibilities, I opted for a classical book.

To date (6 September 2019), this book has served for the following courses:
\begin{itemize}
	\item Course at the Northwest Institute of Eco-Environment and Resources, Lanzhou, China (8 hours, February 2017)
	\item Course at the Universidad Nacional General Sarmiento, Argentina (20 hours, May 2019)
	\item Summer Course at Xiamen University, China (15 hours, July 2019).
	\item Course at Xidian University, China (16 hours, September 2019)
\end{itemize}
I would like to thank the patience of Prof.\ Yie Wu, School of Computer Science, Shaanxi Normal University, Xi'an, for his careful reading and excellent suggestions.

One of the books that exerted the strongest influence in my career was \textit{The Visual Display of Quantitative Information}\cite{Tufte01}.
The choice of style was obvious after knowing that there was one inspired by Edward Tufte's ideas and guidelines, and implemented in \LaTeX.
The patient reader that reached this point has an example of his recommendations put to work.

Writing a book is a frightening task, but I have learned a few lessons from the past, among them:
\begin{itemize}
\item Reading with the eyes of the public helps staying focused.
\item Using \LaTeX\ and \BibTeX\ is absolutely mandatory for quality results.
\item Control version (Git in this case) is a safety net.
\end{itemize}

So here we go with this book.
I hope it will be helpful to those that have the curiosity to browse through its pages.

\vskip5em
\epigraph{Alejandro C.\ Frery}{Macei\'o, 10 October 2017 -- \today}




\mainmatter


\include{Introduction}
\include{ElementsR}
\include{DataFormation}
\include{MultiplicativeModel}
\include{DescriptiveVisualization}
\include{ParameterEstimation}
\include{Applications}
\include{AdvancedTopics}

\backmatter

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\bibliography{./Misc/BookRefs} % Use the bibliography.bib file for the bibliography
\bibliographystyle{plainnat} % Use the plainnat style of referencing

%----------------------------------------------------------------------------------------

\printindex % Print the index at the very end of the document=≠

\end{document}